Models of lens candidates from Space Warps CFHTLS

### 2017-02-15 parts/figures.tex
morphological diagnostics described
editing

\begin{figure*}
\inclGrid{spl-input}
\caption{Nine of the lens candidates marked up with spaghetti
  diagrams.  Red, blue and green dots are proposed locations for
  maxima, minima and saddle points of the arrival time.  The curves
  help guide the placement of the dots, but their precise appearance
  has no significance.  This selection includes the best-modelled
  systems, but also one case (SW57 at upper right) of unsuccessful
  modelling. \label{fig:splinput}}
\end{figure*}

\begin{figure*}
\inclGrid{arrival_spaghetti}
\caption{Arrival-time surfaces of the candidates from
  Figure~\ref{fig:splinput}.
  \label{fig:arriv}}
\end{figure*}

@@

\begin{figure*}
\inclGrid{kappa_map_interpol}
\caption{Mass distribution $\kappa$ in the systems from
  Figures~\ref{fig:splinput}--\ref{fig:synth}.
  \label{fig:kappa}}
\end{figure*}

\begin{figure*}
\inclGrid{kappa_encl}
\caption{Enclosed mass $\kappa$ in the systems from
  Figures~\ref{fig:splinput}--\ref{fig:kappa}.
  \label{fig:encl}}
\end{figure*}

>>>>

\begin{figure*}
\inclGrid{spl-input}
\caption{Nine of the lens candidates marked up with spaghetti
  diagrams.  Red, blue and green dots are proposed locations for
  maxima, minima and saddle points of the arrival time.  The curves
  help guide the placement of the dots, but their precise appearance
  has no significance.  This selection includes the best-modelled
  systems, but also one case (SW57 at upper right) of unsuccessful
  modelling.  Since the modelling process is collaborative among the
  volunteers, with anyone welcome to contribute new models or modify
  existing ones, there are variant spaghetti diagrams for all the
  modelled systems.  The online supplement displays all the models
  presented for discussion during this work.
\label{fig:splinput}}
\end{figure*}

\begin{figure*}
\inclGrid{kappa_map_interpol}
\caption{Mass distribution $\kappa$ in the systems from
  Figures~\ref{fig:splinput}.
\label{fig:kappa}}
\end{figure*}

\begin{figure*}
\inclGrid{kappa_encl}
\caption{Enclosed mass within a given projected radius, expressed as
  the mean $\kappa$ with a given number of arcsec from the centre of
  the lensing galaxy.  The systems are the same as in
  Figures~\ref{fig:splinput}--\ref{fig:kappa}.  The orange band in
  each panel refers to the full ensemble of mass maps in the model,
  while the red curve is the ensemble average.  The dashed vertical
  line indicates the notional Einstein radius, or where the mean
  enclosed $\kappa$ is unity.  The short vertical arrows indicate the
  positions of the images (maxima, saddle points and minima).
  \label{fig:encl}}
\end{figure*}

\begin{figure*}
\inclGrid{arrival_spaghetti}
\caption{Arrival-time surfaces of the systems from
  Figure~\ref{fig:splinput}--\ref{fig:encl}.
  \label{fig:arriv}}
\end{figure*}

@@

### 2017-02-15 parts/massmodel.tex
editing

\section{Mass models}

\begin{figure*}
\includezehn{img/kappa_map/}{_kappa_map}
\caption{\label{fig:kappa}}
\end{figure*}

\begin{figure*}
\includezehn{img/arrival_spaghetti/}{_arrival_spaghetti}
\caption{\label{fig:arriv}}
\end{figure*}

\begin{figure*}
\includeten{img/nsynth/}{_nsynth}
\label{fig:synth}
\caption{}
\end{figure*}

Alongside is a synthetic image produced by modelling.  In it, the
fitted lensed images are shown in colour, while the lensing galaxy and
extraneous objects have been reduced to grayscale.
(Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
synthetic image from another model of the same system.) These two
panels are qualitative and display no units, and moreover, the mutual
alignment of the two panels is only approximate.

\begin{figure*}
\includezehn{img/kappa_encl/}{_kappa_encl}
\caption{}
\end{figure*}

@@

\begin{enumerate}
\item The middle row shows contour maps from the model.  At middle
  left, we have the arrival-time surface.
\item At middle right we have the mass distribution in the usual
  dimensionless form $\kappa$.  Again, these two panels are mainly
  qualitative: both panels are spatially registered and centred on the
  density-peak of the lens, but no scales have been included.
\item The base row supplies spatial and mass scales.  The left panel
  shows the circularly-averaged $\kappa$ of the model ensemble, with
  increasing radius (in arcsec).  The four short vertical lines
  correspond to the minima and saddle points marked in the upper-left
  panel.  The effective Einstein radius \ER is also shown.  As the radius
  scale indicates SW05 is comparatively large lens on the
  sky.
\item 
\end{enumerate}

>>>>

\section{Mass models}\label{sec:massmodels}

Once a spaghetti diagram has been drawn on a web browser, it is
forwarded to a server-side numerical framework, which searches for
mass maps consistent with the given image locations, parities and time
ordering.  The mass maps are made up of mass tiles and are free-form,
but are required to be concentrated around the identified lens centre
\citep[see][for the precise formulation of the search
  problem.]{2014MNRAS.445.2181C} Assuming such mass distributions can
be found (in practise, usually the case) a statistical ensemble of
two-dimensional mass maps is returned.  This ensemble, along with
derived quantities and uncertainties, makes up one SpaghettiLens
model.

The mass distribution will naturally depend on the lens and source
redshifts, which are unknown when a lens candidate is first
identified.  But this is not a problem, because a model can be
trivially rescaled to use better redshift values, as and when they
become available.  This paper uses pipeline photometric redshifts for
the candidate lensing galaxies.  Source redshifts are set to $z=2$
unless an unambiguous photometric redshift is available.

Figure~\ref{fig:kappa}

Figure~\ref{fig:encl} shows the circularly-averaged $\kappa$ of the
model ensemble, with increasing radius (in arcsec).  The effective
Einstein radius \ER is also shown.

Figure~\ref{fig:arriv}

Figure~\ref{fig:synth}
New method, see also Figure~\figref{synthimg} in
Appendix~\ref{subsec:sourcefit}.

\endinput

  The ensemble average
can, however, be a useful representative of the whole ensemble.  The
user interface of SpaghettiLens returns graphical representations of
the ensemble-average mass map and some derived quantities to the
modeller for review.  The modeller can post these results on a forum,
or discard them and try again.  Other volunteers can start the
modelling process afresh, or they can take an existing model from the
forum and modify its input spaghetti diagram or its accompanying
options, and thus obtain a revised model.

Alongside is a synthetic image produced by modelling.  In it, the
fitted lensed images are shown in colour, while the lensing galaxy and
extraneous objects have been reduced to grayscale.
) These two
panels are qualitative and display no units, and moreover, the mutual
alignment of the two panels is only approximate.

@@

\begin{enumerate}
\item The middle row shows contour maps from the model.  At middle
  left, we have the arrival-time surface.
\item At middle right we have the mass distribution in the usual
  dimensionless form $\kappa$.  Again, these two panels are mainly
  qualitative: both panels are spatially registered and centred on the
  density-peak of the lens, but no scales have been included.
\item The base row supplies spatial and mass scales.  The left panel

\item 
\end{enumerate}
